---
title: |
  <center> S-052: Intermediate and Advanced Statistical Methods </center>
  <center> for Applied Educational Research </center>
  <center> Fall, 2023 </center>
author: "Jacob Wolf and Hwa Pyung Yoo"
date: "December 2023"
output: html_document
---

###RQ: TODO?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load in packages

```{r packages, warning = FALSE, message = FALSE}
require(foreign)
require(tidyverse)
require(lme4)
require(stargazer)
require(haven)
require(gridExtra)
require(Hmisc)
#install.packages("datawizard")
require(datawizard)
#install.packages("ggpubr")
require(ggpubr)
```

##Define the local directory and Import Data

```{r setwd}
setwd("/Users/jacobwolf/Desktop/Harvard/classes/s052/s52-final-project")
load("WVS_Cross-National_Wave_7_rData_v5_0.rdata", dat <- new.env())
dat <- dat[["WVS_Cross-National_Wave_7_v5_0"]]
```

# Data cleaning

```{r clean}
# create binary variable for regime type [0==non-dem; 1==dem]
dat$regime_bin <- ifelse(dat$regtype >=1 & dat$regtype <= 3, 0, ifelse(dat$regtype >= 4 & dat$regtype <= 5, 1, NA)) %>% factor()

dat_countries <- dat[match(unique(dat$B_COUNTRY_ALPHA), dat$B_COUNTRY_ALPHA),]
```

## Rescaling and demeaning individual-level variables
```{r rescale_individual}

#RESCALE
dat_transformed <- dat

# Procedural democracy understanding var (Q243)
dat_transformed$proc_dem <- replace(dat$Q243, dat$Q243 < 0, NA)

# Liberal democracy understanding var (Q246)
dat_transformed$lib_dem <- replace(dat$Q246, dat$Q246 < 0, NA)

# Social media for politics var (Q217)
dat_transformed$sm_pol <- replace(dat$Q217, dat$Q217 < 0, NA)
dat_transformed <- transform(dat_transformed, sm_pol = abs((sm_pol - 1)-2))

# Higher ed variable (Q275)
dat_transformed$higher_ed <- ifelse(dat$Q275 < 0, NA, ifelse(dat$Q275 >= 0 & dat$Q275 < 5, 0, ifelse(dat$Q275 >= 5, 1, dat$Q275)))

# Age var (Q262)
dat_transformed$age <- replace(dat$Q262, dat$Q262 < 0, NA)

# Sex var (Q260)
dat_transformed$sex <- replace(dat$Q260, dat$Q260 < 0, NA)
dat_transformed <- transform(dat_transformed, sex = abs((sex - 1) - 1))

# Income var (Q288)
dat_transformed$income <- replace(dat$Q288, dat$Q288 < 0, NA)

# Urban/rural var (H_URBRURAL)
dat_transformed$H_URBRURAL <- replace(dat$H_URBRURAL, dat$H_URBRURAL < 0, NA)
dat_transformed <- transform(dat_transformed, urban = abs((H_URBRURAL - 1)-1))

# Rescaling gdp
dat_transformed <- transform(dat_transformed, GDPpercap1_scaled = GDPpercap1/1e9)


# DEMEANING for dem and non-dem countries
# split into dem and non-dem for summary stats (i.e. demean only within dempcracies)
dat_transformed_nondem <- filter(dat_transformed, dat_transformed$regime_bin==0)
dat_transformed_dem <- filter(dat_transformed, dat_transformed$regime_bin==1)

# Procedural democracy understanding var (Q243)
dat_transformed_nondem <- transform(dat_transformed_nondem, proc_dem_demeaned = proc_dem-mean(proc_dem, na.rm=TRUE))
dat_transformed_dem <- transform(dat_transformed_dem, proc_dem_demeaned = proc_dem-mean(proc_dem, na.rm=TRUE))

# Liberal democracy understanding var (Q246)
dat_transformed_nondem <- transform(dat_transformed_nondem, lib_dem_demeaned = lib_dem-mean(lib_dem, na.rm=TRUE))
dat_transformed_dem <- transform(dat_transformed_dem, lib_dem_demeaned = lib_dem-mean(lib_dem, na.rm=TRUE))

# Social media for politics var (Q217)
dat_transformed_nondem <- transform(dat_transformed_nondem, sm_pol_demeaned = sm_pol-mean(sm_pol, na.rm=TRUE))
dat_transformed_dem <- transform(dat_transformed_dem, sm_pol_demeaned = sm_pol-mean(sm_pol, na.rm=TRUE))

# Higher ed variable (Q275)
dat_transformed_nondem <- transform(dat_transformed_nondem, higher_ed_demeaned = higher_ed-mean(higher_ed, na.rm=TRUE))
dat_transformed_dem <- transform(dat_transformed_dem, higher_ed_demeaned = higher_ed-mean(higher_ed, na.rm=TRUE))

#Create a variable representing each country's average score and standard deviation for Mundlak
dat_transformed_nondem <- dat_transformed_nondem %>%
  group_by(B_COUNTRY_ALPHA) %>%
  mutate(higher_ed_avg = mean(higher_ed, na.rm = TRUE),
         higher_ed_sd = sd(higher_ed, na.rm = TRUE),
         sm_pol_avg = mean(sm_pol, na.rm = TRUE),
         sm_pol_sd = sd(sm_pol, na.rm = TRUE),
         sm_pol_demeaned_avg = mean(sm_pol_demeaned, na.rm = TRUE),
         sm_pol_demeaned_sd = sd(sm_pol_demeaned, na.rm = TRUE),
         proc_dem_avg = mean(proc_dem, na.rm = TRUE),
         proc_dem_sd = sd(proc_dem, na.rm = TRUE),
         proc_dem_demeaned_avg = mean(proc_dem_demeaned, na.rm = TRUE),
         proc_dem_demeaned_sd = sd(proc_dem_demeaned, na.rm = TRUE),
         lib_dem_avg = mean(lib_dem, na.rm = TRUE),
         lib_dem_sd = sd(lib_dem, na.rm = TRUE),
         lib_dem_demeaned_avg = mean(lib_dem_demeaned, na.rm = TRUE),
         lib_dem_demeaned_sd = sd(lib_dem_demeaned, na.rm = TRUE)
        )
dat_transformed_nondem <- as.data.frame(dat_transformed_nondem)

dat_transformed_dem <- dat_transformed_dem %>%
  group_by(B_COUNTRY_ALPHA) %>%
  mutate(higher_ed_avg = mean(higher_ed, na.rm = TRUE),
         higher_ed_sd = sd(higher_ed, na.rm = TRUE),
         sm_pol_avg = mean(sm_pol, na.rm = TRUE),
         sm_pol_sd = sd(sm_pol, na.rm = TRUE),
         sm_pol_demeaned_avg = mean(sm_pol_demeaned, na.rm = TRUE),
         sm_pol_demeaned_sd = sd(sm_pol_demeaned, na.rm = TRUE),
         proc_dem_avg = mean(proc_dem, na.rm = TRUE),
         proc_dem_sd = sd(proc_dem, na.rm = TRUE),
         proc_dem_demeaned_avg = mean(proc_dem_demeaned, na.rm = TRUE),
         proc_dem_demeaned_sd = sd(proc_dem_demeaned, na.rm = TRUE),
         lib_dem_avg = mean(lib_dem, na.rm = TRUE),
         lib_dem_sd = sd(lib_dem, na.rm = TRUE),
         lib_dem_demeaned_avg = mean(lib_dem_demeaned, na.rm = TRUE),
         lib_dem_demeaned_sd = sd(lib_dem_demeaned, na.rm = TRUE)
        )
dat_transformed_dem <- as.data.frame(dat_transformed_dem)


```

## Transforming country-level variables
```{r rescale_country}
dat_countries_nondem <- dat_transformed_nondem[match(unique(dat_transformed_nondem$B_COUNTRY_ALPHA), dat_transformed_nondem$B_COUNTRY_ALPHA),]
dat_countries_dem <- dat_transformed_dem[match(unique(dat_transformed_dem$B_COUNTRY_ALPHA), dat_transformed_dem$B_COUNTRY_ALPHA),]


#Rescale GDP
dat_countries_nondem <- transform(dat_countries_nondem, GDPpercap1_scaled = GDPpercap1/1e9)
dat_countries_dem <- transform(dat_countries_dem, GDPpercap1_scaled = GDPpercap1/1e9)

```


# EDA

## Histograms
### Understanding of democracy
```{r hist_dem}
non_dem_proc_dem <- ggplot(dat_transformed_nondem, aes(x = proc_dem)) + 
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth = 1) + 
  scale_y_continuous(labels = scales::percent) +
  geom_vline(xintercept = mean(dat_transformed_nondem$proc_dem, na.rm = TRUE), color = "red") + 
  annotate("text", x=mean(dat_transformed_nondem$proc_dem, na.rm = TRUE)-2, y=.3, label=paste(c("mean:", format(round(mean(dat_transformed_nondem$proc_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  geom_vline(xintercept = median(dat_transformed_nondem$proc_dem, na.rm = TRUE), color = "blue") + 
  annotate("text", x=median(dat_transformed_nondem$proc_dem, na.rm = TRUE)-2, y=.2, label=paste(c("median:", format(round(median(dat_transformed_nondem$proc_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="blue") +
  xlab("Procedural democracy in non-democracy") +
  ylab("Percentage of Responses")

dem_proc_dem <- ggplot(dat_transformed_dem, aes(x = proc_dem)) + 
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth = 1) + 
  scale_y_continuous(labels = scales::percent) +
  geom_vline(xintercept = mean(dat_transformed_dem$proc_dem, na.rm = TRUE), color = "red") + 
  geom_vline(xintercept = median(dat_transformed_dem$proc_dem, na.rm = TRUE), color = "blue") + 
  annotate("text", x=mean(dat_transformed_dem$proc_dem, na.rm = TRUE)-2, y=.3, label=paste(c("mean:", format(round(mean(dat_transformed_dem$proc_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  annotate("text", x=median(dat_transformed_dem$proc_dem, na.rm = TRUE)-2, y=.2, label=paste(c("median:", format(round(median(dat_transformed_dem$proc_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="blue") +
  xlab("Procedural democracy in democracy") +
  ylab("Percentage of Responses")


non_dem_lib_dem <- ggplot(dat_transformed_nondem, aes(x = lib_dem)) + 
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth = 1) + 
  scale_y_continuous(labels = scales::percent) +
  geom_vline(xintercept = mean(dat_transformed_nondem$lib_dem, na.rm = TRUE), color = "red") + 
  annotate("text", x=mean(dat_transformed_nondem$lib_dem, na.rm = TRUE)-2, y=.3, label=paste(c("mean:", format(round(mean(dat_transformed_nondem$lib_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  geom_vline(xintercept = median(dat_transformed_nondem$lib_dem, na.rm = TRUE), color = "blue") + 
  annotate("text", x=median(dat_transformed_nondem$lib_dem, na.rm = TRUE)-2, y=.2, label=paste(c("median:", format(round(median(dat_transformed_nondem$lib_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="blue") +
  xlab("Liberal democracy in non-democracy") +
  ylab("Percentage of Responses")

dem_lib_dem <- ggplot(dat_transformed_dem, aes(x = lib_dem)) + 
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth = 1) + 
  scale_y_continuous(labels = scales::percent) +  
  geom_vline(xintercept = mean(dat_transformed_dem$lib_dem, na.rm = TRUE), color = "red") + 
  annotate("text", x=mean(dat_transformed_dem$lib_dem, na.rm = TRUE)-2, y=.3, label=paste(c("mean:", format(round(mean(dat_transformed_dem$lib_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  geom_vline(xintercept = median(dat_transformed_dem$lib_dem, na.rm = TRUE), color = "blue") + 
  annotate("text", x=median(dat_transformed_dem$lib_dem, na.rm = TRUE)-2, y=.2, label=paste(c("median:", format(round(median(dat_transformed_dem$lib_dem, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="blue") +
  xlab("Liberal democracy in democracy") +
  ylab("Percentage of Responses")

grid.arrange(non_dem_proc_dem, dem_proc_dem, non_dem_lib_dem, dem_lib_dem, ncol=2)
```

### Social media use for political purposes and higher ed
```{r hist_pred}
non_dem_sm_pol <- ggplot(dat_transformed_nondem, aes(x = sm_pol)) + 
  geom_histogram(binwidth = 1) + 
  geom_vline(xintercept = mean(dat_transformed_nondem$sm_pol, na.rm = TRUE), color = "red") + 
  annotate("text", x=mean(dat_transformed_nondem$sm_pol, na.rm = TRUE)-.5, y=600, label=paste(c("mean:", format(round(mean(dat_transformed_nondem$sm_pol, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  #geom_vline(xintercept = median(dat_transformed_nondem$sm_pol, na.rm = TRUE), color = "blue") + 
  #annotate("text", x=median(dat_transformed_nondem$sm_pol, na.rm = TRUE)-.7, y=1000, label=paste(c("median:", format(round(median(dat_transformed_nondem$sm_pol, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="blue") +
  xlab("Social Media Use in non-democracy") +
  ylab("Count")

dem_sm_pol <- ggplot(dat_transformed_dem, aes(x = sm_pol)) + 
  geom_histogram(binwidth = 1) + 
  geom_vline(xintercept = mean(dat_transformed_dem$sm_pol, na.rm = TRUE), color = "red") + 
  annotate("text", x=mean(dat_transformed_dem$sm_pol, na.rm = TRUE)-.5, y=900, label=paste(c("mean:", format(round(mean(dat_transformed_dem$sm_pol, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  xlab("Social Media Use in democracy") +
  ylab("Count")


non_dem_higher_ed <- ggplot(dat_transformed_nondem, aes(x = higher_ed)) + 
  geom_histogram(binwidth = 1) + 
  geom_vline(xintercept = mean(dat_transformed_nondem$higher_ed, na.rm = TRUE), color = "red") + 
  annotate("text", x=mean(dat_transformed_nondem$higher_ed, na.rm = TRUE)-.5, y=900, label=paste(c("mean:", format(round(mean(dat_transformed_nondem$higher_ed, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  xlab("Higher Ed in non-democracy") +
  ylab("Count")

dem_higher_ed <- ggplot(dat_transformed_dem, aes(x = higher_ed)) + 
  geom_histogram(binwidth = 1) + 
  geom_vline(xintercept = mean(dat_transformed_dem$higher_ed, na.rm = TRUE), color = "red") +
  annotate("text", x=mean(dat_transformed_dem$higher_ed, na.rm = TRUE)-.5, y=1800, label=paste(c("mean:", format(round(mean(dat_transformed_dem$higher_ed, na.rm = TRUE), 2), nsmall = 2)), collapse = " "), color="red") +
  xlab("Higher ed in democracy") +
  ylab("Count")


grid.arrange(non_dem_sm_pol, dem_sm_pol, non_dem_higher_ed, dem_higher_ed, ncol=2)
```

## Scatter: 
### Recreating country avg understanding scatterplots
``` {r scatter_democracy_understanding}

# Understanding of Procedural Democracy for non-democracies
nondem_proc_dem_plot <- ggplot(dat_countries_nondem, aes(x = proc_dem_avg, y = B_COUNTRY_ALPHA, xmin = proc_dem_avg-proc_dem_sd, xmax = proc_dem_avg+proc_dem_sd)) +
        # geom_line() +
        geom_point() +
        #geom_errorbarh(height=.2) +
        #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
        #geom_vline(xintercept = 81.5, col = "red") +
        #ylim(0, 1) +
        xlim(0, 10) +
        xlab("Avg Understanding (Procedural)") +
        ylab("Country") +
        labs(title = "Non-Democracies") +
        theme(axis.text.y=element_text(size=4))

dem_proc_dem_plot <- ggplot(dat_countries_dem, aes(x = proc_dem_avg, y = B_COUNTRY_ALPHA, xmin = proc_dem_avg-proc_dem_sd, xmax = proc_dem_avg+proc_dem_sd)) +
      # geom_line() +
      geom_point() +
      #geom_errorbarh(height=.2) +
      #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
      #geom_vline(xintercept = 81.5, col = "red") +
      #ylim(0, 1) +
      xlim(0, 10) +
      xlab("Avg Understanding (Procedural)") +
      ylab("Country") +
      labs(title = "Democracies") +
      theme(axis.text.y=element_text(size=4))

nondem_lib_dem_plot <- ggplot(dat_countries_nondem, aes(x = lib_dem_avg, y = B_COUNTRY_ALPHA, xmin = lib_dem_avg-lib_dem_sd, xmax = lib_dem_avg+lib_dem_sd)) +
      # geom_line() +
      geom_point() +
      #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
      #geom_vline(xintercept = 81.5, col = "red") +
      #ylim(0, 1) +
      xlim(0, 10) +
      xlab("Avg Understanding (Liberal)") +
      ylab("Country") +
      labs(title = "Non-Democracies") +
      theme(axis.text.y=element_text(size=4))

dem_lib_dem_plot <- ggplot(dat_countries_dem,  aes(x = lib_dem_avg, y = B_COUNTRY_ALPHA, xmin = lib_dem_avg-lib_dem_sd, xmax = lib_dem_avg+lib_dem_sd)) +
      # geom_line() +
      geom_point() +
      #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
      #geom_vline(xintercept = 81.5, col = "red") +
      #ylim(0, 1) +
      xlim(0, 10) +
      xlab("Avg Understanding (Liberal)") +
      ylab("Country") +
      labs(title = "Democracies") +
      theme(axis.text.y=element_text(size=4))

grid.arrange(nondem_proc_dem_plot, dem_proc_dem_plot, nondem_lib_dem_plot, dem_lib_dem_plot, ncol=2)
```

### Scatter Social Media and Higher ed by country
``` {r scatter_sm_higher_ed}

# Social Media for non-democracies
nondem_smpol_plot <- ggplot(dat_countries_nondem, aes(x = sm_pol_avg, y = B_COUNTRY_ALPHA)) +
        # geom_line() +
        geom_point() +
        #geom_errorbarh(height=.2) +
        #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
        #geom_vline(xintercept = 81.5, col = "red") +
        #ylim(0, 1) +
        xlim(0, 1.75) +
        xlab("Avg Social Media Use") +
        ylab("Country") +
        labs(title = "Non-Democracies") +
        theme(axis.text.y=element_text(size=4))

# Social Media for democracies
dem_smpol_plot <- ggplot(dat_countries_dem, aes(x = sm_pol_avg, y = B_COUNTRY_ALPHA)) +
        # geom_line() +
        geom_point() +
        #geom_errorbarh(height=.2) +
        #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
        #geom_vline(xintercept = 81.5, col = "red") +
        #ylim(0, 1) +
        xlim(0, 1.75) +
        xlab("Avg Social Media Use") +
        ylab("Country") +
        labs(title = "Democracies") +
        theme(axis.text.y=element_text(size=4))

# Higher ed for non-democracies
nondem_highered_plot <- ggplot(dat_countries_nondem, aes(x = higher_ed_avg, y = B_COUNTRY_ALPHA)) +
        # geom_line() +
        geom_point() +
        #geom_errorbarh(height=.2) +
        #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
        #geom_vline(xintercept = 81.5, col = "red") +
        #ylim(0, 1) +
        xlim(0, .75) +
        xlab("Avg Higher Ed") +
        ylab("Country") +
        labs(title = "Non-Democracies") +
        theme(axis.text.y=element_text(size=4))

# Higher ed for democracies
dem_highered_plot <- ggplot(dat_countries_dem, aes(x = higher_ed_avg, y = B_COUNTRY_ALPHA)) +
        # geom_line() +
        geom_point() +
        #geom_errorbarh(height=.2) +
        #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
        #geom_vline(xintercept = 81.5, col = "red") +
        #ylim(0, 1) +
        xlim(0, .75) +
        xlab("Avg Higher Ed") +
        ylab("Country") +
        labs(title = "Democracies") +
        theme(axis.text.y=element_text(size=4))

grid.arrange(nondem_smpol_plot, dem_smpol_plot, nondem_highered_plot, dem_highered_plot, ncol=2)
```

### Scatter Plots Social Media Vs. Understanding of Democracy
```{r scatter_vars}
non_dem_proc_dem <- ggplot(dat_transformed_nondem, aes(x = sm_pol, y = proc_dem)) + 
  geom_bin2d() +
  theme_bw() +
  xlab("Social Media Use") +
  ylab("Proc. dem. in non-dem.")

dem_proc_dem <- ggplot(dat_transformed_dem, aes(x = sm_pol, y = proc_dem)) + 
  geom_bin2d() +
  theme_bw() +
  xlab("Social Media Use") +
  ylab("Proc dem. in dem.")

non_dem_lib_dem <- ggplot(dat_transformed_nondem, aes(x = sm_pol, y = lib_dem)) + 
  geom_bin2d() +
  theme_bw() +
  xlab("Social Media Use") +
  ylab("Lib dem in non-dem.")

dem_lib_dem <- ggplot(dat_transformed_dem, aes(x = sm_pol, y = lib_dem)) + 
  geom_bin2d() +
  theme_bw() +
  xlab("Social Media Use") +
  ylab("Liberal dem. in dem.")

grid.arrange(non_dem_proc_dem, dem_proc_dem, non_dem_lib_dem, dem_lib_dem, ncol=2)
```

# Checking stats with paper

``` {r stats}
dat_nondem <- subset(dat_transformed[c("proc_dem", "lib_dem", "sm_pol", "higher_ed", "age", "sex","income", "urban")], dat_transformed$regime_bin==0)
dat_countries_nondem <- subset(dat_countries[c("GDPpercap1", "v2mecenefi")], dat_countries$regime_bin==0)
dat_dem <- subset(dat_transformed[c("proc_dem", "lib_dem", "sm_pol", "higher_ed", "age", "sex","income", "urban")], dat_transformed$regime_bin==1)

# NOTE: SOMETHING HAPPENING THAT MAKES dat_countries have different obersvations than filtered dat_tranformed
dat_countries_dem <- subset(dat_countries[c("GDPpercap1", "v2mecenefi")], dat_countries$regime_bin==1)

stargazer(dat_nondem,
          type = "text", 
          title="Summary of statistics individual-level variables for non-democracies",
          #column.labels=c("Observations", "Mean", "Standard Deviation", "Minimum", "Maximum"),
          covariate.labels=c("Procedural democracy","Liberal democracy", "Social Media for pol", "Higher education", "Age", "Male", "Income", "Urban"),
          align=TRUE)

stargazer(dat_countries_nondem,
          type = "text", 
          title="Summary of statistics country-level variables for non-democracies",
          #column.labels=c("Observations", "Mean", "Standard Deviation", "Minimum", "Maximum"),
          covariate.labels=c("GDP", "Internet Censorship"),
          align=TRUE)


stargazer(dat_dem,
          type = "text", 
          title="Summary of statistics individual-level variables for democracies",
          #column.labels=c("Observations", "Mean", "Standard Deviation", "Minimum", "Maximum"),
          covariate.labels=c("Procedural democracy","Liberal democracy", "Social Media for pol", "Higher education", "Age", "Male", "Income", "Urban"),
          align=TRUE)

stargazer(dat_countries_dem,
          type = "text", 
          title="Summary of statistics country-level variables for democracies",
          #column.labels=c("Observations", "Mean", "Standard Deviation", "Minimum", "Maximum"),
          covariate.labels=c("GDP", "Internet Censorship"),
          align=TRUE)
```

# Model building

## model 0 -- single predictor

### simple model
``` {r simple-0}

#Model 0 - Understanding of procedural democracy in Non-Democracies
simple_mod0 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(simple_mod0)


simple_reg_0 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +
  #ggplot(aes(x=sm_pol, y=proc_dem, group=higher_ed)) + 
  #geom_line(size=2, aes(color=higher_ed))+
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = dat_transformed_nondem) +  #add scatterplot at individual level for higher ed, color red

  geom_abline(aes(intercept = fixef(simple_mod0)[1],     # intercept
                  slope = fixef(simple_mod0)[2], color="Higher Ed"), lwd = 1) + #add reference line for higher ed

  #geom_point(aes(x = country_sm_avg, y = proc_dem)) + #add scatterplot at country level, point color defaults to black
  #geom_abline(aes(intercept = fixef(mod0)[1], slope = (fixef(mod0)[2] + fixef(mod0)[5])), lwd = 1) + #add reference line
  scale_colour_manual("", 
                      breaks = c("Higher Ed", "No Higher Ed"),
                      values = c("red", "blue")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Non-Democracies")

simple_reg_0
```

### Mundlak Model
``` {r mund-0}
#Model 0 - Understanding of procedural democracy in Non-Democracies
mund_mod0 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned + sm_pol_demeaned_avg + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(mund_mod0)

mund_reg_0 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +
  #ggplot(aes(x=sm_pol, y=proc_dem, group=higher_ed)) + 
  #geom_line(size=2, aes(color=higher_ed))+
  
  # INDIVIDUAL LEVEL
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = dat_transformed_nondem) +  #add scatterplot at individual level for higher ed, color red

  # higher ed individual line
  geom_abline(aes(intercept =
                    fixef(mund_mod0)[1],      # Intercept 
              slope = 
                    fixef(mund_mod0)[2],      # sm_pol
              color="Individual-Level"), lwd = 1) + 
  
  # COUNTRY LEVEL
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "pink", data = dat_transformed_nondem) + #add scatterplot at country level for countries with >=50% individuals with higher ed, color pink
  
  # higher ed countries line
  geom_abline(aes(intercept =
                    fixef(mund_mod0)[1],      # Intercept 
              slope = 
                    fixef(mund_mod0)[2] +      # sm_pol
                    fixef(mund_mod0)[3],       # country sm average
              color="Country-Level"), lwd = 1) +

  scale_colour_manual("", 
                      breaks = c("Individual-Level", "Country-Level"),
                      values = c("red", "pink")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Understanding of Democracy (Procedural Democracy)") +
  ggtitle("mundlak")

mund_reg_0
```

## model 1 -- two predictors

### simple model
``` {r simple-1}

#Model 1 - Understanding of procedural democracy in Non-Democracies
simple_mod1 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned + higher_ed + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(simple_mod0)


simple_reg_1 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_mod1)[1] +     # intercept
                              fixef(simple_mod1)[3],     # higher ed
                  slope = fixef(simple_mod1)[2], color="Higher Ed"), lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_mod1)[1],     # intercept
                  slope = fixef(simple_mod1)[2], color="No Higher Ed"), lwd = 1) + #add reference line


  scale_colour_manual("", 
                      breaks = c("Higher Ed", "No Higher Ed"),
                      values = c("red", "blue")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Non-Democracies")

simple_reg_1
```

### Mundlak Model
``` {r mund-1}

#Model 1 - Understanding of procedural democracy in Non-Democracies
mund_mod1 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned + higher_ed + sm_pol_demeaned_avg + higher_ed_avg + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(simple_mod0)

# filter data to use in country level -- cutoff at median
#country_higher_ed_dat <- filter(dat_transformed, dat_transformed$higher_ed_avg >= median(dat_countries_nondem$higher_ed_avg))
#country_no_higher_ed_dat <- filter(dat_transformed, dat_transformed$higher_ed_avg < median(dat_countries_nondem$higher_ed_avg))

# filter data to use in country level -- cutoff at majority
country_nondem_higher_ed_dat <- filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed_avg >= .5)
country_nondem_no_higher_ed_dat <- filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed_avg < .5)

mund_reg_1 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # INDIVIDUAL LEVEL
  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_mod1)[1] +     # intercept
                              fixef(mund_mod1)[3],     # higher ed
                  slope = fixef(mund_mod1)[2], color="Individual-Level, Higher Ed"), lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_mod1)[1],     # intercept
                  slope = fixef(mund_mod1)[2], color="Individual-Level, No Higher Ed"), lwd = 1) + #add reference line

 # COUNTRY LEVEL
  #higher ed >= median country higher ed)
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "pink", data = country_nondem_higher_ed_dat)  + #add scatterplot 
  
  geom_abline(aes(intercept =
                    fixef(mund_mod1)[1] +      # Intercept 
                    fixef(mund_mod1)[3]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +      # higher ed
                    fixef(mund_mod1)[5]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE),       # higher ed avg
              slope = 
                    fixef(mund_mod1)[2] +      # sm_pol
                    fixef(mund_mod1)[4],       # country sm average
              color="Country-Level, Above Med. Higher Ed"), lwd = 1) +
  
  #higher ed < median country higher ed)
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "lightblue", data = country_nondem_no_higher_ed_dat)  + #add scatterplot 
  
  geom_abline(aes(intercept =
                    fixef(mund_mod1)[1] +      # Intercept 
                    fixef(mund_mod1)[3]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +      # higher ed
                    fixef(mund_mod1)[5]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE),       # higher ed avg
              slope = 
                    fixef(mund_mod1)[2] +      # sm_pol
                    fixef(mund_mod1)[4],       # country sm average
              color="Country-Level, Below Med. Higher Ed"), lwd = 1) +
  
  scale_colour_manual("", 
                      breaks = c("Individual-Level, Higher Ed", "Individual-Level, No Higher Ed", "Country-Level, Above Med. Higher Ed", "Country-Level, Below Med. Higher Ed"),
                      values = c("red", "blue", "pink", "lightblue")) +

  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Non-Democracies")

mund_reg_1
```

## Model 2 - level 1 Interaction term

### simple
``` {r simple-2}

#Model 2 - Understanding of procedural democracy in Non-Democracies
simple_mod2 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned*higher_ed + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(simple_mod2)


simple_reg_2 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_mod2)[1] +     # intercept
                              fixef(simple_mod2)[3],     # higher ed
                  slope =     fixef(simple_mod2)[2] +        # social media
                              fixef(simple_mod2)[4],       # social media*higher ed
                  color="Higher Ed"), lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_mod2)[1],     # intercept
                  slope = fixef(simple_mod2)[2], color="No Higher Ed"), lwd = 1) + #add reference line


  scale_colour_manual("", 
                      breaks = c("Higher Ed", "No Higher Ed"),
                      values = c("red", "blue")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Non-Democracies")

simple_reg_2
```


### Mundlak Model
``` {r mund-2}

#Model 2 - Understanding of procedural democracy in Non-Democracies
mund_mod2 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned*higher_ed + sm_pol_demeaned_avg*higher_ed_avg + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(mund_mod2)


mund_reg_2 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # INDIVIDUAL LEVEL
  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_mod2)[1] +     # intercept
                              fixef(mund_mod2)[3],      # higher ed
                  slope     = fixef(mund_mod2)[2] +     # social media
                              fixef(mund_mod2)[6],      # social media*higher ed
                  color="Individual-Level, Higher Ed"), lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_mod2)[1],     # intercept
                  slope = fixef(mund_mod2)[2], color="Individual-Level, No Higher Ed"), lwd = 1) + #add reference line

 # COUNTRY LEVEL 
 # higher ed above median
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "pink", data = country_nondem_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept =
                    fixef(mund_mod2)[1] +      # Intercept 
                    fixef(mund_mod2)[3]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +      # higher ed
                    fixef(mund_mod2)[5]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE),       # higher ed avg
              slope = 
                    fixef(mund_mod2)[2] +      # sm_pol
                    fixef(mund_mod2)[4] +      # country sm average
                    fixef(mund_mod2)[6]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                    fixef(mund_mod2)[7]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol

              color="Country-Level, Above Med. Higher Ed"), lwd = 1) +
  
   # higher ed below median
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "lightblue", data = country_nondem_no_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept =
                    fixef(mund_mod2)[1] +      # Intercept 
                    fixef(mund_mod2)[3]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +      # higher ed
                    fixef(mund_mod2)[5]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE),       # higher ed avg
              slope = 
                    fixef(mund_mod2)[2] +      # sm_pol
                    fixef(mund_mod2)[4] +      # country sm average
                    fixef(mund_mod2)[6]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                    fixef(mund_mod2)[7]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol

              color="Country-Level, Below Med. Higher Ed"), lwd = 1) +
  
  scale_colour_manual("", 
                      breaks = c("Individual-Level, Higher Ed", "Individual-Level, No Higher Ed", "Country-Level, Above Med. Higher Ed", "Country-Level, Below Med. Higher Ed"),
                      values = c("red", "blue", "pink", "lightblue")) +

  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Non-Democracies")

mund_reg_2
```

## Model 3 - adding controls

### simple
``` {r simple-proc-nondem-3}

#Model 3 - Understanding of procedural democracy in Non-Democracies
simple_proc_nondem_mod3 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned*higher_ed + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(simple_proc_nondem_mod3)


simple_proc_nondem_reg_3 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_proc_nondem_mod3)[1] +     # intercept
                              fixef(simple_proc_nondem_mod3)[3] +     # higher ed
                              fixef(simple_proc_nondem_mod3)[4]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_proc_nondem_mod3)[5] +     # sex (set to male)
                              fixef(simple_proc_nondem_mod3)[6]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(simple_proc_nondem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_proc_nondem_mod3)[8]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_proc_nondem_mod3)[9]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_proc_nondem_mod3)[2] +        # social media
                              fixef(simple_proc_nondem_mod3)[10],       # social media*higher ed
                  color="Higher Ed"), lty = 2, lwd = 1) + # add reference line
    
  
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_proc_nondem_mod3)[1] +     # intercept
                              fixef(simple_proc_nondem_mod3)[4]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_proc_nondem_mod3)[5] +     # sex (set to male)
                              fixef(simple_proc_nondem_mod3)[6]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(simple_proc_nondem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_proc_nondem_mod3)[8]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_proc_nondem_mod3)[9]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_proc_nondem_mod3)[2],        # social media
                  color="No Higher Ed"), lwd = 1) + #add reference line


  scale_colour_manual("", 
                      breaks = c("Higher Ed", "No Higher Ed"),
                      values = c("red", "blue")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Non-Democracies")

simple_proc_nondem_reg_3
```

### Mundlak
``` {r mund-3}

#Model 3 - Understanding of procedural democracy in Non-Democracies
mund_proc_nondem_mod3 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned*higher_ed + sm_pol_demeaned_avg*higher_ed_avg + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(mund_proc_nondem_mod3)


mund_proc_nondem_reg_3 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # INDIVIDUAL LEVEL
  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_proc_nondem_mod3)[1] +     # intercept
                              fixef(mund_proc_nondem_mod3)[3] +     # higher ed
                              fixef(mund_proc_nondem_mod3)[6]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_nondem_mod3)[8]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_nondem_mod3)[10]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_nondem_mod3)[11]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_proc_nondem_mod3)[2] +        # social media
                              fixef(mund_proc_nondem_mod3)[12],       # social media*higher ed
                  color="Individual-Level, Higher Ed"), lty = 2, lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_proc_nondem_mod3)[1] +     # intercept
                              fixef(mund_proc_nondem_mod3)[6]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_nondem_mod3)[8]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_nondem_mod3)[10]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_nondem_mod3)[11]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_proc_nondem_mod3)[2],        # social media
                  color="Individual-Level, No Higher Ed"), lwd = 1) + #add reference line

 # COUNTRY LEVEL 
 # higher ed above median
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "pink", data = country_nondem_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_proc_nondem_mod3)[1] +      # Intercept 
                              fixef(mund_proc_nondem_mod3)[3]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_proc_nondem_mod3)[5]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_proc_nondem_mod3)[6]*mean(country_nondem_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_nondem_mod3)[8]*mean(country_nondem_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_nondem_mod3)[10]*mean(country_nondem_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_nondem_mod3)[11]*mean(country_nondem_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_proc_nondem_mod3)[2] +      # sm_pol
                              fixef(mund_proc_nondem_mod3)[4] +      # country sm average
                              fixef(mund_proc_nondem_mod3)[12]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_proc_nondem_mod3)[13]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                    color="Country-Level, Maj. Higher Ed"), lty = 2,lwd = 1) +
  
   # higher ed below median
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "lightblue", data = country_nondem_no_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_proc_nondem_mod3)[1] +      # Intercept 
                              fixef(mund_proc_nondem_mod3)[3]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_proc_nondem_mod3)[5]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_proc_nondem_mod3)[6]*mean(country_nondem_no_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_nondem_mod3)[8]*mean(country_nondem_no_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_nondem_mod3)[10]*mean(country_nondem_no_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_nondem_mod3)[11]*mean(country_nondem_no_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_proc_nondem_mod3)[2] +      # sm_pol
                              fixef(mund_proc_nondem_mod3)[4] +      # country sm average
                              fixef(mund_proc_nondem_mod3)[12]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_proc_nondem_mod3)[13]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                  color="Country-Level, Maj. No Higher Ed"), lwd = 1) +
  
  scale_colour_manual("", 
                      breaks = c("Individual-Level, Higher Ed", "Individual-Level, No Higher Ed", "Country-Level, Maj. Higher Ed", "Country-Level, Maj. No Higher Ed"),
                      values = c("red", "blue", "pink", "lightblue")) +

  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Non-Democracies")

mund_proc_nondem_reg_3
```

```{r model-tables}
stargazer(mund_mod0, mund_mod1, mund_mod2, mund_mod3, 
          #type = "text",
          type = "html", 
          out="proc-dem-non-dem.html",
          title = "Understanding of Democracy in Non-Democracies with Mundlak Specification",
          dep.var.labels = c("Understanding of Democracy (Procedural Democracy)"),
          column.labels = c("Single Predictor (Model 0)", "Dual Predictor (Model 1)", "Interaction (Model 2)", "Interaction with Controls (Model 3)"),
          model.numbers = FALSE,
          digits=4,
          covariate.labels=c("Social Media Use","Higher Ed Attainment", "Social Media*Higher Ed", "Country Avg Social Media Use", "Country Avg Higher Ed", "Country Avg Social Media*Avg Higher Ed", "Age", "Male", "Income", "Urbanity", "Country GDP", "Country Internet Censorship"),
          order=c("^sm_pol_demeaned$", "^higher_ed$", "^sm_pol_demeaned:higher_ed$", "^sm_pol_demeaned_avg$", "^higher_ed_avg$", "^sm_pol_demeaned_avg:higher_ed_avg$",  "age", "sex", "income", "urban", "GDPpercap1_scaled", "v2mecenefi")
          #keep.stat = c("n"),
          #add.lines = list(c("neg2ll", neg2ll),
           #                c("sigmau", sigma_u),
            #               c("sigmae", sigma_e),
             #              c("sigma2u", sigma2_u),
              #             c("sigma2e", sigma2_e))
          )
```
# Understanding of Procedural Dem for Democracies

``` {r filter-dem-higher-ed}
# filter data to use in country level -- cutoff at majority
country_dem_higher_ed_dat <- filter(dat_transformed_dem, dat_transformed_dem$higher_ed_avg >= .5)
country_dem_no_higher_ed_dat <- filter(dat_transformed_dem, dat_transformed_dem$higher_ed_avg < .5)
```

## Model 3 - adding controls

### simple
``` {r simple-proc-dem-3}

#Model 3 - Understanding of procedural democracy in Democracies
simple_proc_dem_mod3 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned*higher_ed + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_dem, REML = FALSE)
summary(simple_proc_dem_mod3)


simple_proc_dem_reg_3 <- dat_transformed_dem%>%
  #filter(plotrange) %>%
  ggplot() +

  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_proc_dem_mod3)[1] +     # intercept
                              fixef(simple_proc_dem_mod3)[3] +     # higher ed
                              fixef(simple_proc_dem_mod3)[4]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_proc_dem_mod3)[5] +     # sex (set to male)
                              fixef(simple_proc_dem_mod3)[6]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(simple_proc_dem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_proc_dem_mod3)[8]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_proc_dem_mod3)[9]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_proc_dem_mod3)[2] +        # social media
                              fixef(simple_proc_dem_mod3)[10],       # social media*higher ed
                  color="Higher Ed"),lty = 2, lwd = 1) + # add reference line
    
  
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_proc_dem_mod3)[1] +     # intercept
                              fixef(simple_proc_dem_mod3)[4]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_proc_dem_mod3)[5] +     # sex (set to male)
                              fixef(simple_proc_dem_mod3)[6]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(simple_proc_dem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_proc_dem_mod3)[8]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_proc_dem_mod3)[9]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_proc_dem_mod3)[2],        # social media
                  color="No Higher Ed"), lwd = 1) + #add reference line


  scale_colour_manual("", 
                      breaks = c("Higher Ed", "No Higher Ed"),
                      values = c("red", "blue")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Democracies")

simple_proc_dem_reg_3
```
### Mundlak
``` {r mund-proc-dem-3}

#Model 3 - Understanding of procedural democracy in Democracies
mund_proc_dem_mod3 <- lmer(proc_dem_demeaned ~ sm_pol_demeaned*higher_ed + sm_pol_demeaned_avg*higher_ed_avg + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_dem, REML = FALSE)
summary(mund_proc_dem_mod3)


mund_proc_dem_reg_3 <- dat_transformed_dem%>%
  #filter(plotrange) %>%
  ggplot() +

  # INDIVIDUAL LEVEL
  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_proc_dem_mod3)[1] +     # intercept
                              fixef(mund_proc_dem_mod3)[3] +     # higher ed
                              fixef(mund_proc_dem_mod3)[6]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_dem_mod3)[8]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_dem_mod3)[10]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_dem_mod3)[11]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_proc_dem_mod3)[2] +        # social media
                              fixef(mund_proc_dem_mod3)[12],       # social media*higher ed
                  color="Individual-Level, Higher Ed"), lty = 2, lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_proc_dem_mod3)[1] +     # intercept
                              fixef(mund_proc_dem_mod3)[6]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_dem_mod3)[8]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_dem_mod3)[10]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_dem_mod3)[11]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_proc_dem_mod3)[2],        # social media
                  color="Individual-Level, No Higher Ed"), lwd = 1) + #add reference line

 # COUNTRY LEVEL 
 # higher ed above median
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "pink", data = country_dem_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_proc_dem_mod3)[1] +      # Intercept 
                              fixef(mund_proc_dem_mod3)[3]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_proc_dem_mod3)[5]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_proc_dem_mod3)[6]*mean(country_dem_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_dem_mod3)[8]*mean(country_dem_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_dem_mod3)[10]*mean(country_dem_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_dem_mod3)[11]*mean(country_dem_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_proc_dem_mod3)[2] +      # sm_pol
                              fixef(mund_proc_dem_mod3)[4] +      # country sm average
                              fixef(mund_proc_dem_mod3)[12]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_proc_dem_mod3)[13]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                    color="Country-Level, Maj. Higher Ed"), lty = 2, lwd = 1) +
  
   # higher ed below median
  geom_point(aes(x = sm_pol_demeaned_avg, y = proc_dem_demeaned_avg), col = "lightblue", data = country_dem_no_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_proc_dem_mod3)[1] +      # Intercept 
                              fixef(mund_proc_dem_mod3)[3]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_proc_dem_mod3)[5]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_proc_dem_mod3)[6]*mean(country_dem_no_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_proc_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_proc_dem_mod3)[8]*mean(country_dem_no_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_proc_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_proc_dem_mod3)[10]*mean(country_dem_no_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_proc_dem_mod3)[11]*mean(country_dem_no_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_proc_dem_mod3)[2] +      # sm_pol
                              fixef(mund_proc_dem_mod3)[4] +      # country sm average
                              fixef(mund_proc_dem_mod3)[12]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_proc_dem_mod3)[13]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                  color="Country-Level, Maj. No Higher Ed"), lwd = 1) +
  
  scale_colour_manual("", 
                      breaks = c("Individual-Level, Higher Ed", "Individual-Level, No Higher Ed", "Country-Level, Maj. Higher Ed", "Country-Level, Maj. No Higher Ed"),
                      values = c("red", "blue", "pink", "lightblue")) +

  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Democracies")

mund_proc_dem_reg_3
```
# Liberal Dem in Non-Dems

## Model 3

### Simple
``` {r simple-proc-dem-3}

#Model 3 - Understanding of procedural democracy in Democracies
simple_lib_nondem_mod3 <- lmer(lib_dem_demeaned ~ sm_pol_demeaned*higher_ed + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(simple_lib_nondem_mod3)


simple_lib_nondem_reg_3 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_lib_nondem_mod3)[1] +     # intercept
                              fixef(simple_lib_nondem_mod3)[3] +     # higher ed
                              fixef(simple_lib_nondem_mod3)[4]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_lib_nondem_mod3)[5] +     # sex (set to male)
                              fixef(simple_lib_nondem_mod3)[6]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(simple_lib_nondem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_lib_nondem_mod3)[8]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_lib_nondem_mod3)[9]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_lib_nondem_mod3)[2] +        # social media
                              fixef(simple_lib_nondem_mod3)[10],       # social media*higher ed
                  color="Higher Ed"), lty = 2, lwd = 1) + # add reference line
    
  
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(proc_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_lib_nondem_mod3)[1] +     # intercept
                              fixef(simple_lib_nondem_mod3)[4]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_lib_nondem_mod3)[5] +     # sex (set to male)
                              fixef(simple_lib_nondem_mod3)[6]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(simple_lib_nondem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_lib_nondem_mod3)[8]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_lib_nondem_mod3)[9]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_lib_nondem_mod3)[2],        # social media
                  color="No Higher Ed"), lwd = 1) + #add reference line


  scale_colour_manual("", 
                      breaks = c("Higher Ed", "No Higher Ed"),
                      values = c("red", "blue")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Democracies")

simple_lib_nondem_reg_3
```

### Mundlak
``` {r mund-lib-nondem-3}

#Model 3 - Understanding of liberal democracy in Non-Democracies
mund_lib_nondem_mod3 <- lmer(lib_dem_demeaned ~ sm_pol_demeaned*higher_ed + sm_pol_demeaned_avg*higher_ed_avg + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_nondem, REML = FALSE)
summary(mund_lib_nondem_mod3)


mund_lib_nondem_reg_3 <- dat_transformed_nondem%>%
  #filter(plotrange) %>%
  ggplot() +

  # INDIVIDUAL LEVEL
  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(lib_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_lib_nondem_mod3)[1] +     # intercept
                              fixef(mund_lib_nondem_mod3)[3] +     # higher ed
                              fixef(mund_lib_nondem_mod3)[6]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_nondem_mod3)[8]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_nondem_mod3)[10]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_nondem_mod3)[11]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_lib_nondem_mod3)[2] +        # social media
                              fixef(mund_lib_nondem_mod3)[12],       # social media*higher ed
                  color="Individual-Level, Higher Ed"), lty = 2, lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(lib_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_nondem, dat_transformed_nondem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_lib_nondem_mod3)[1] +     # intercept
                              fixef(mund_lib_nondem_mod3)[6]*mean(dat_transformed_nondem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_nondem_mod3)[8]*mean(dat_transformed_nondem$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_nondem_mod3)[10]*mean(dat_transformed_nondem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_nondem_mod3)[11]*mean(dat_transformed_nondem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_lib_nondem_mod3)[2],        # social media
                  color="Individual-Level, No Higher Ed"), lwd = 1) + #add reference line

 # COUNTRY LEVEL 
 # higher ed above median
  geom_point(aes(x = sm_pol_demeaned_avg, y = lib_dem_demeaned_avg), col = "pink", data = country_nondem_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_lib_nondem_mod3)[1] +      # Intercept 
                              fixef(mund_lib_nondem_mod3)[3]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_lib_nondem_mod3)[5]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_lib_nondem_mod3)[6]*mean(country_nondem_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_nondem_mod3)[8]*mean(country_nondem_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_nondem_mod3)[10]*mean(country_nondem_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_nondem_mod3)[11]*mean(country_nondem_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_lib_nondem_mod3)[2] +      # sm_pol
                              fixef(mund_lib_nondem_mod3)[4] +      # country sm average
                              fixef(mund_lib_nondem_mod3)[12]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_lib_nondem_mod3)[13]*mean(country_nondem_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                    color="Country-Level, Maj. Higher Ed"), lty = 2, lwd = 1) +
  
   # higher ed below median
  geom_point(aes(x = sm_pol_demeaned_avg, y = lib_dem_demeaned_avg), col = "lightblue", data = country_nondem_no_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_lib_nondem_mod3)[1] +      # Intercept 
                              fixef(mund_lib_nondem_mod3)[3]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_lib_nondem_mod3)[5]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_lib_nondem_mod3)[6]*mean(country_nondem_no_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_nondem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_nondem_mod3)[8]*mean(country_nondem_no_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_nondem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_nondem_mod3)[10]*mean(country_nondem_no_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_nondem_mod3)[11]*mean(country_nondem_no_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_lib_nondem_mod3)[2] +      # sm_pol
                              fixef(mund_lib_nondem_mod3)[4] +      # country sm average
                              fixef(mund_lib_nondem_mod3)[12]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_lib_nondem_mod3)[13]*mean(country_nondem_no_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                  color="Country-Level, Maj. No Higher Ed"), lwd = 1) +
  
  scale_colour_manual("", 
                      breaks = c("Individual-Level, Higher Ed", "Individual-Level, No Higher Ed", "Country-Level, Maj. Higher Ed", "Country-Level, Maj. No Higher Ed"),
                      values = c("red", "blue", "pink", "lightblue")) +

  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Liberal Democracy") +
  ggtitle("Non-Democracies")

mund_lib_nondem_reg_3
```
# Liberal Democracy in Democracies

## Model 3

### simple
``` {r simple-proc-dem-3}

#Model 3 - Understanding of procedural democracy in Democracies
simple_lib_dem_mod3 <- lmer(lib_dem_demeaned ~ sm_pol_demeaned*higher_ed + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_dem, REML = FALSE)
summary(simple_lib_dem_mod3)


simple_lib_dem_reg_3 <- dat_transformed_dem%>%
  #filter(plotrange) %>%
  ggplot() +

  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(lib_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_lib_dem_mod3)[1] +     # intercept
                              fixef(simple_lib_dem_mod3)[3] +     # higher ed
                              fixef(simple_lib_dem_mod3)[4]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_lib_dem_mod3)[5] +     # sex (set to male)
                              fixef(simple_lib_dem_mod3)[6]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(simple_lib_dem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_lib_dem_mod3)[8]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_lib_dem_mod3)[9]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_lib_dem_mod3)[2] +        # social media
                              fixef(simple_lib_dem_mod3)[10],       # social media*higher ed
                  color="Higher Ed"), lty = 2, lwd = 1) + # add reference line
    
  
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(lib_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(simple_lib_dem_mod3)[1] +     # intercept
                              fixef(simple_lib_dem_mod3)[4]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(simple_lib_dem_mod3)[5] +     # sex (set to male)
                              fixef(simple_lib_dem_mod3)[6]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(simple_lib_dem_mod3)[7] +     # urban (set to urban)
                              fixef(simple_lib_dem_mod3)[8]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(simple_lib_dem_mod3)[9]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(simple_lib_dem_mod3)[2],        # social media
                  color="No Higher Ed"), lwd = 1) + #add reference line


  scale_colour_manual("", 
                      breaks = c("Higher Ed", "No Higher Ed"),
                      values = c("red", "blue")) +
  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Procedural Democracy") +
  ggtitle("Democracies")

simple_lib_dem_reg_3
```

### Mundlak
``` {r mund-lib-dem-3}

#Model 3 - Understanding of liberal democracy in Democracies
mund_lib_dem_mod3 <- lmer(lib_dem_demeaned ~ sm_pol_demeaned*higher_ed + sm_pol_demeaned_avg*higher_ed_avg + age + sex+ income + urban + GDPpercap1_scaled + v2mecenefi + (1|B_COUNTRY_ALPHA), data = dat_transformed_dem, REML = FALSE)
summary(mund_lib_dem_mod3)


mund_lib_dem_reg_3 <- dat_transformed_dem%>%
  #filter(plotrange) %>%
  ggplot() +

  # INDIVIDUAL LEVEL
  # higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(lib_dem_demeaned)), col = "red", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==1)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_lib_dem_mod3)[1] +     # intercept
                              fixef(mund_lib_dem_mod3)[3] +     # higher ed
                              fixef(mund_lib_dem_mod3)[6]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_dem_mod3)[8]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_dem_mod3)[10]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_dem_mod3)[11]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_lib_dem_mod3)[2] +        # social media
                              fixef(mund_lib_dem_mod3)[12],       # social media*higher ed
                  color="Individual-Level, Higher Ed"), lty = 2, lwd = 1) + # add reference line
    
    # no higher ed
  geom_point(aes(x = jitter(sm_pol_demeaned), y = jitter(lib_dem_demeaned)), col = "blue", cex = 0.1, data = filter(dat_transformed_dem, dat_transformed_dem$higher_ed==0)) +  #add scatterplot

  geom_abline(aes(intercept = fixef(mund_lib_dem_mod3)[1] +     # intercept
                              fixef(mund_lib_dem_mod3)[6]*mean(dat_transformed_dem$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_dem_mod3)[8]*mean(dat_transformed_dem$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_dem_mod3)[10]*mean(dat_transformed_dem$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_dem_mod3)[11]*mean(dat_transformed_dem$v2mecenefi, na.rm=TRUE),     # internet censorship

                  slope =     fixef(mund_lib_dem_mod3)[2],        # social media
                  color="Individual-Level, No Higher Ed"), lwd = 1) + #add reference line

 # COUNTRY LEVEL 
 # higher ed above median
  geom_point(aes(x = sm_pol_demeaned_avg, y = lib_dem_demeaned_avg), col = "pink", data = country_dem_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_lib_dem_mod3)[1] +      # Intercept 
                              fixef(mund_lib_dem_mod3)[3]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_lib_dem_mod3)[5]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_lib_dem_mod3)[6]*mean(country_dem_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_dem_mod3)[8]*mean(country_dem_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_dem_mod3)[10]*mean(country_dem_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_dem_mod3)[11]*mean(country_dem_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_lib_dem_mod3)[2] +      # sm_pol
                              fixef(mund_lib_dem_mod3)[4] +      # country sm average
                              fixef(mund_lib_dem_mod3)[12]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_lib_dem_mod3)[13]*mean(country_dem_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                    color="Country-Level, Maj. Higher Ed"), lty = 2, lwd = 1) +
  
   # higher ed below median
  geom_point(aes(x = sm_pol_demeaned_avg, y = lib_dem_demeaned_avg), col = "lightblue", data = country_dem_no_higher_ed_dat) + #add scatterplot 
  
  geom_abline(aes(intercept = fixef(mund_lib_dem_mod3)[1] +      # Intercept 
                              fixef(mund_lib_dem_mod3)[3]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher ed
                              fixef(mund_lib_dem_mod3)[5]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +       # higher ed avg
                              fixef(mund_lib_dem_mod3)[6]*mean(country_dem_no_higher_ed_dat$age, na.rm=TRUE) +     # age (set to mean)
                              fixef(mund_lib_dem_mod3)[7] +     # sex (set to male)
                              fixef(mund_lib_dem_mod3)[8]*mean(country_dem_no_higher_ed_dat$income, na.rm=TRUE) +     # income
                              fixef(mund_lib_dem_mod3)[9] +     # urban (set to urban)
                              fixef(mund_lib_dem_mod3)[10]*mean(country_dem_no_higher_ed_dat$GDPpercap1_scaled, na.rm=TRUE) +     # gdp (set to avg)
                              fixef(mund_lib_dem_mod3)[11]*mean(country_dem_no_higher_ed_dat$v2mecenefi, na.rm=TRUE),     # internet censorship
                    slope =   fixef(mund_lib_dem_mod3)[2] +      # sm_pol
                              fixef(mund_lib_dem_mod3)[4] +      # country sm average
                              fixef(mund_lib_dem_mod3)[12]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE) +     # higher_ed*sm_pol
                              fixef(mund_lib_dem_mod3)[13]*mean(country_dem_no_higher_ed_dat$higher_ed, na.rm=TRUE),      # avg_higher_ed*avg_sm_pol
                  color="Country-Level, Maj. No Higher Ed"), lwd = 1) +
  
  scale_colour_manual("", 
                      breaks = c("Individual-Level, Higher Ed", "Individual-Level, No Higher Ed", "Country-Level, Maj. Higher Ed", "Country-Level, Maj. No Higher Ed"),
                      values = c("red", "blue", "pink", "lightblue")) +

  #xlim(c(-4, 4)) +
  xlab("Use of social media for political purposes") +
  ylab("Liberal Democracy") +
  ggtitle("Democracies")

mund_lib_dem_reg_3
```

``` {r all-simple}
ggarrange(simple_proc_nondem_reg_3, simple_proc_dem_reg_3, simple_lib_nondem_reg_3, simple_lib_dem_reg_3, ncol=2, nrow=2, common.legend = TRUE, legend="right")
```

```{r all-simple-stargazer}

# Shortening length of var names to avoid stargazer error
m1 <- simple_proc_nondem_mod3
m2 <- simple_proc_dem_mod3
m3 <- simple_lib_nondem_mod3
m4 <- simple_lib_dem_mod3

stargazer(m1, m2, m3, m4,
          type = "text",
          #type = "html", 
          #out="simple.html",
          title = "Understanding of democracy, social media, and higher education",
          dep.var.labels = c("Understanding of Democracy (Procedural Democracy)", "Understanding of Democracy (Liberal Democracy)"),
          column.labels = c("Non-democracy", "Democracy", "Non-Democracy", "Democracy"),
          model.numbers = FALSE,
          digits=4,
          covariate.labels=c("Social Media Use","Higher Ed Attainment", "Social Media*Higher Ed", "Age", "Male", "Income", "Urbanity", "Country GDP", "Country Internet Censorship"),
          order=c("^sm_pol_demeaned$", "^higher_ed$", "^sm_pol_demeaned:higher_ed$",  "age", "sex", "income", "urban", "GDPpercap1_scaled", "v2mecenefi")
          )
```

```{r all-mund-stargazer}
# Shortening length of var names to avoid stargazer error
m1 <- mund_proc_nondem_mod3
m2 <- mund_proc_dem_mod3
m3 <- mund_lib_nondem_mod3
m4 <- mund_lib_dem_mod3

stargazer(m1, m2, m3, m4, 
          type = "text",
          #type = "html", 
          #out="mund.html",
          title = "Understanding of democracy, social media, and higher education",
          dep.var.labels = c("Understanding of Democracy (Procedural Democracy)", "Understanding of Democracy (Liberal Democracy)"),
          column.labels = c("Non-democracy", "Democracy", "Non-Democracy", "Democracy"),
          model.numbers = FALSE,
          digits=4,
          covariate.labels=c("Social Media Use","Higher Ed Attainment", "Social Media*Higher Ed", "Country Avg Social Media Use", "Country Avg Higher Ed", "Country Avg Social Media*Avg Higher Ed", "Age", "Male", "Income", "Urbanity", "Country GDP", "Country Internet Censorship"),
          order=c("^sm_pol_demeaned$", "^higher_ed$", "^sm_pol_demeaned:higher_ed$", "^sm_pol_demeaned_avg$", "^higher_ed_avg$", "^sm_pol_demeaned_avg:higher_ed_avg$",  "age", "sex", "income", "urban", "GDPpercap1_scaled", "v2mecenefi")
          )
```

``` {r all-mundlak}
ggarrange(mund_proc_nondem_reg_3, mund_proc_dem_reg_3, mund_lib_nondem_reg_3, mund_lib_dem_reg_3, ncol=2, nrow=2, common.legend = TRUE, legend="right")
```
# extra stuff

```{r boxes}
# Understanding of Procedural Democracy for non-democracies
plot0 <- filter(dat_transformed, dat_transformed$regime_bin==0) %>%
    group_by(B_COUNTRY_ALPHA) %>%
      #summarize(meanunderstanding = mean(proc_dem, na.rm = TRUE)) %>%
      ggplot(aes(x = B_COUNTRY_ALPHA, y = proc_dem)) +
      geom_boxplot() +
      # geom_line() +
      #geom_point() +
      #geom_errorbarh(height=.2) +
      #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
      #geom_vline(xintercept = 81.5, col = "red") +
      #ylim(0, 1) +
      #xlim(0, 10) +
      ylab("Avg Understanding") +
      xlab("Country") +
      labs(title = "Proc Dem. in Non-Dem.")

# Understanding of Procedural Democracy for democracies
plot1 <- filter(dat_transformed, dat_transformed$regime_bin==1) %>%
    group_by(B_COUNTRY_ALPHA) %>%
      #summarize(meanunderstanding = mean(proc_dem, na.rm = TRUE)) %>%
      ggplot(aes(x = B_COUNTRY_ALPHA, y = proc_dem)) +
      geom_boxplot() +
      # geom_line() +
      #geom_point() +
      #geom_errorbarh(height=.2) +
      #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
      #geom_vline(xintercept = 81.5, col = "red") +
      #ylim(0, 1) +
      #xlim(0, 10) +
      ylab("Avg Understanding") +
      xlab("Country") +
      labs(title = "Proc Dem. in Dem.")

# Understanding of Liberal Democracy for non-democracies
plot2 <- filter(dat_transformed, dat_transformed$regime_bin==0) %>%
    group_by(B_COUNTRY_ALPHA) %>%
      #summarize(meanunderstanding = mean(proc_dem, na.rm = TRUE)) %>%
      ggplot(aes(x = B_COUNTRY_ALPHA, y = lib_dem)) +
      geom_boxplot() +
      # geom_line() +
      #geom_point() +
      #geom_errorbarh(height=.2) +
      #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
      #geom_vline(xintercept = 81.5, col = "red") +
      #ylim(0, 1) +
      #xlim(0, 10) +
      ylab("Avg Understanding") +
      xlab("Country") +
      labs(title = "Lib. Dem. in Non-Dem.")

# Understanding of Liberal Democracy for democracies
plot3 <- filter(dat_transformed, dat_transformed$regime_bin==1) %>%
    group_by(B_COUNTRY_ALPHA) %>%
      #summarize(meanunderstanding = mean(proc_dem, na.rm = TRUE)) %>%
      ggplot(aes(x = B_COUNTRY_ALPHA, y = lib_dem)) +
      geom_boxplot() +
      # geom_line() +
      #geom_point() +
      #geom_errorbarh(height=.2) +
      #geom_abline(mapping = NULL, data = NULL, slope = 0.474, intercept = 1.230) +
      #geom_vline(xintercept = 81.5, col = "red") +
      #ylim(0, 1) +
      #xlim(0, 10) +
      ylab("Avg Understanding") +
      xlab("Country") +
      labs(title = "Lib. Dem. in Dem.")

grid.arrange(plot0, plot1, plot2, plot3, ncol=2)
```

``` {r extras-0}
#NUM OBSERVATIONS
#23,049 individual observations from non-democracies;
nrow(dat_filtered[dat_filtered$regime_bin == 0,])
#50,985 observations from democracies
nrow(dat_filtered[dat_filtered$regime_bin == 1,])

# AVG RESPONSES
# Social media use: 0.68 in non-democracies and 0.88 in democracies; 
mean(dat_filtered[dat_filtered$regime_bin == 0,]$Q217)
mean(dat_filtered[dat_filtered$regime_bin == 1,]$Q217)
#Higher Education: 31% in non-democracies and 33% in democracies
mean(dat_filtered[dat_filtered$regime_bin == 0,]$higher_ed)
mean(dat_filtered[dat_filtered$regime_bin == 1,]$higher_ed)

for (country_code in unique(filter(dat, dat$regime_bin==1 | dat$regime_bin==0)$B_COUNTRY_ALPHA)) {
  print(country_code)
  print(unique(filter(dat, dat$B_COUNTRY_ALPHA==country_code)$GDPpercap1))
}


for (country_code in unique(filter(dat, dat$regime_bin==1 | dat$regime_bin==0)$B_COUNTRY_ALPHA)) {
  print(country_code)
  print(unique(filter(dat, dat$B_COUNTRY_ALPHA==country_code)$v2mecenefi))
}
```

```{r extras-1}
col = "regime_bin"
dat_filtered <- dat %>%
  filter(dat[col] == 1 | dat[col] == 0)
```

```{r extras-2}
# trying to filter 
dat_filter_all <- dat
for(col_name in colnames(dat)[1:50]) {
  dat_filter_all <- dat_filter_all %>%
    filter(dat_filter_all[col_name] != -1, dat_filter_all[col_name] != -2, dat_filter_all[col_name] != -3, dat_filter_all[col_name] != -4, dat_filter_all[col_name] != -5)
  print(col_name)
}
```
